### 2025-01-21 ECE159 Lecture Notes/main.tex
added link to github
gitignore

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf ECE 159 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Fundamentals of Electric Circuits, Winter 2024 \hfill ECE 159\\
\vspace{10pt}
\section{Basic Concepts}
\subsection{Basic Defintions}
\begin{definition}[Voltage]
    The difference of the electric potential between two points in a circuit. The enegy required to move a charge from one point to another.
    \begin{equation}
        V \defeq \int_C \textbf{E} \cdot d\textbf{l} = \frac{dW}{dq}
    \end{equation}
    \end{definition}
    \paragraph{Polarity} The polarity is fliped as illustrated when the voltage is indicated as negative.
    \begin{definition}[Current]
    Rate of change of charge at a particular point in the circuit.
    \begin{equation}
        I \defeq \frac{dq}{dt}
    \end{equation}
    \end{definition}

@@

\paragraph{Electromotive Force (emf) / Voltage} Work is performed by 
the electric field to move a charge from one point to another. 
The work done per unit charge is the voltage.
\begin{equation}
    \text{Voltage} = \frac{\Delta W}{q}
\end{equation}
\subsection{Power and Energy}
\paragraph{Power} To relate power to  voltage and current, we can use the following equation:
\begin{equation}
    P \defeq \frac{dW}{dt} = \frac{dW}{dq} \cdot \frac{dq}{dt} = V \cdot I
\end{equation}
\paragraph{Sign} If $P = V \cdot I > 0$, the element is delivering power. If $P = V \cdot I < 0$, the element is absorbing power.
\paragraph{Energy}  the energy absorbed or supplied by an element
from time $t_0$ to time $t_1$ is:
\begin{equation}
    W = \int_{t_0}^{t_1} P(t) dt
\end{equation}
\subsection{Circuit Elements}
\paragraph{Active Elements} Active elements are sources of energy. They can deliver power to the circuit. While passive elements are elements that can only absorb power.
\paragraph{Ideal Sources} Ideal sources are sources that provide a set voltage or current regardless of what it is connected to. We often assume that sources are ideal.
\paragraph{Independent Sources} Independent sources are sources that provide a set voltage or current regardless of what it is connected to.
\paragraph{Dependent Sources} Dependent sources are sources that provide a voltage or current to the circuit depending on another voltage or current in the circuit.
\paragraph{Resistor} A resistor is a circuit element that restricts the flow of charge. The voltage across a resistor is proportional to the current through it.

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\paragraph{Voltage Division} The voltage across a resistor in series is proportional to the resistance of the resistor.
\begin{equation}
    V_i = V \frac{R_i}{R_{\text{eq}}}
\end{equation}
\paragraph{Current Division} The current through a resistor in parallel is proportional to the conductance of the resistor.
\begin{equation}
    I_i = I \frac{G_i}{G_{\text{eq}}}
\end{equation}
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\subsection{Kirchhoff's Laws}
\paragraph{} Kirchhoff's Laws are two laws that are used to analyze electric circuits.
\paragraph{Kirchhoff's Current Law (KCL)} The sum of currents entering a node is equal to the sum of currents leaving a node.
\begin{equation}
    \sum I_{\text{in}} = \sum I_{\text{out}}
\end{equation}
\paragraph{Kirchhoff's Voltage Law (KVL)} The sum of voltages around a closed loop is equal to zero.
\begin{equation}
    \sum V_{\text{loop}} = 0
\end{equation}

\section{DC Circuits}
\paragraph{}

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf ECE 159 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Fundamentals of Electric Circuits, Winter 2024 \hfill ECE 159\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\
\vspace{10pt}
\section{Basic Concepts}
\subsection{Basic Defintions}
\begin{definition}[Voltage]
    The difference of the electric potential between two points in a circuit. The enegy required to move a charge from one point to another.
    \begin{equation}
        V \defeq \int_C \textbf{E} \cdot d\textbf{l} = \frac{dW}{dq}
    \end{equation}
    \end{definition}
    \paragraph{Polarity} The polarity is fliped as illustrated when the voltage is indicated as negative.
    \begin{definition}[Current]
    Rate of change of charge at a particular point in the circuit.
    \begin{equation}
        I \defeq \frac{dq}{dt}
    \end{equation}
    \end{definition}

@@

\paragraph{Electromotive Force (emf) / Voltage} Work is performed by 
the electric field to move a charge from one point to another. 
The work done per unit charge is the voltage.
\begin{equation}
    \text{Voltage} = \frac{\Delta W}{q}
\end{equation}
\subsection{Power and Energy}
\paragraph{Power} To relate power to  voltage and current, we can use the following equation:
\begin{equation}
    P \defeq \frac{dW}{dt} = \frac{dW}{dq} \cdot \frac{dq}{dt} = V \cdot I
\end{equation}
\paragraph{Sign} If $P = V \cdot I > 0$, the element is delivering power. If $P = V \cdot I < 0$, the element is absorbing power.
\paragraph{Energy}  the energy absorbed or supplied by an element
from time $t_0$ to time $t_1$ is:
\begin{equation}
    W = \int_{t_0}^{t_1} P(t) dt
\end{equation}
\section{DC Circuits}
\subsection{Circuit Elements}
\paragraph{Active Elements} Active elements are sources of energy. They can deliver power to the circuit. While passive elements are elements that can only absorb power.
\paragraph{Ideal Sources} Ideal sources are sources that provide a set voltage or current regardless of what it is connected to. We often assume that sources are ideal.
\paragraph{Independent Sources} Independent sources are sources that provide a set voltage or current regardless of what it is connected to.
\paragraph{Dependent Sources} Dependent sources are sources that provide a voltage or current to the circuit depending on another voltage or current in the circuit.
\paragraph{Resistor} A resistor is a circuit element that restricts the flow of charge. The voltage across a resistor is proportional to the current through it.

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\paragraph{Voltage Division} The voltage across a resistor in series is proportional to the resistance of the resistor.
\begin{equation}
    V_i = V \frac{R_i}{R_{\text{eq}}}
\end{equation}
\paragraph{Current Division} The current through a resistor in parallel is proportional to the conductance of the resistor.
\begin{equation}
    I_i = I \frac{G_i}{G_{\text{eq}}}
\end{equation}
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\subsection{Kirchhoff's Laws}
\paragraph{} Kirchhoff's Laws are two laws that are used to analyze electric circuits.
\paragraph{Kirchhoff's Current Law (KCL)} The sum of currents entering a node is equal to the sum of currents leaving a node.
\begin{equation}
    \sum I_{\text{in}} = \sum I_{\text{out}} \quad \text{or} \quad \sum_\text{$n$ in node} I_n = 0
\end{equation}
\paragraph{Node Analysis} Node Analysis is a method used to analyze electric circuits by writing KCL equations at each node.
\paragraph{Ground Node} Ground is a reference point in a circuit. It is often used as a reference point for voltage.
\paragraph{Kirchhoff's Voltage Law (KVL)} The sum of voltages around a closed loop is equal to zero.
\begin{equation}
    \sum_\text{$n$ in loop} V_{n} = 0
\end{equation}
\paragraph{Mesh Analysis} Mesh Analysis is a method used to analyze electric circuits by writing KVL equations for each loop.
\paragraph{Multiple Meshes} To analyze a circuit with multiple meshes, write KVL equations for each mesh and KCL equations for each node. There would be times where we add currents via KCL equations.
\paragraph{}

### 2025-01-21 linalgA1/main.tex
gitignore

% Student 1
\fbox{
  \begin{minipage}{\textwidth}
    \vspace{0.75cm}
    \makebox[\textwidth]{\large Full Name: Cheung, Hei Shing\enspace\hrulefill}\\[0.75cm]
    \makebox[\textwidth]{\large Student number: 101090782\enspace\hrulefill}\\
  \end{minipage}
}

@@

% Student 2
\fbox{
  \begin{minipage}{\textwidth}
    \vspace{0.75cm}
    \makebox[\textwidth]{\large Full Name:\enspace\hrulefill}\\[0.75cm]
    \makebox[\textwidth]{\large Student number:\enspace\hrulefill}\\
  \end{minipage}
}

@@

    %%% Your work goes here!  
   \paragraph{} We prove that $B = \varnothing$. Assume, for the sake of contradiction, that $B \neq \varnothing$. Then there exists a point $(a,b,c) \in B$ such that
       $\mathcal{B}_1$, $\mathcal{B}_2$, and $\mathcal{B}_3$ are \textbf{TRUE}. Thus:
       \begin{itemize}
        \item For all $\beta \in \mathbb{R}$, $\beta\mathcal{B}_2: 11\beta a + 7\beta b + 3\beta c = 15\beta$ is \textbf{TRUE}; also
        \item $\mathcal{B}_3$ is \textbf{TRUE}. 
       \end{itemize}
    Hence, $\mathcal{B}_3 - \beta \mathcal{B}_2$ is \textbf{TRUE} for all $\beta \in \mathbb{R}$. This implies there exist $(a,b,c)$ s.t.: $3a + 2b + c = 5$ is \textbf{TRUE}. It follows from $\mathcal{A}_3: 3a + 2b + c = 5$ and that $\mathcal{B}_2 = \mathcal{A}_2$ and that $\mathcal{B}_1 = \mathcal{A}_1$ are all \textbf{TRUE}. Thus, $A \neq \varnothing$, a contradiction. Therefore, $B = \varnothing$.

@@

   \textcolor{black}{ \underline{case 2: $B = \varnothing$} }
   %%% Do not change the height of this box. Your work must fit inside it.
  \makenonemptybox{130pt}{
   %%% Your work goes here!  
   \paragraph{} We prove that $A = \varnothing$. Assume, for the sake of contradiction, that $A \neq \varnothing$. Then there exists a point $(a,b,c) \in A$ such that $\mathcal{A}_1$, $\mathcal{A}_2$, and $\mathcal{A}_3$ are \textbf{TRUE}. Thus:
       \begin{itemize}
        \item For all $\beta \in \mathbb{R}$, $\beta\mathcal{A}_2: 11\beta a + 7\beta b + 3\beta c = 15\beta$ is \textbf{TRUE}; also
        \item $\mathcal{A}_3$ is \textbf{TRUE}. 
       \end{itemize}
    Hence, $\mathcal{B}_3 = \mathcal{A}_3 + \beta \mathcal{A}_2$ is \textbf{TRUE} for all $\beta \in \mathbb{R}$. It follows from $\mathcal{A}_2 = \mathcal{B}_2$ and that $\mathcal{A}_1 = \mathcal{B}_1$ are all \textbf{TRUE}. Thus, $B \neq \varnothing$, a contradiction. Therefore, $A = \varnothing$.
% end of your answer to case 2 unless you need to continue the answer on page 4
}

@@

   %%% Do not change the height of this box. Your work must fit inside it.
  \makenonemptybox{25pt}{ 
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    $\alpha \in \mathbb{R}$
    %%% end of your answer    
  }

@@

  \subpart Under what conditions on $\alpha$ is $C \subseteq A$? \textit{No justification needed,
just one complete sentence.} \vspace{.15in}
\makenonemptybox{25pt}{ 
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    $\alpha \neq 0$
    %%% end of your answer    
  }

@@

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{200pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't

@@

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{400pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    %%% run into the next question or off the bottom of the page (and don't get too close to the bottom
    %%% either, please!)

@@

 % mark option as correct by using \CorrectChoice
\begin{checkboxes}
  \choice True
  \choice False
\end{checkboxes}

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{150pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    %%% run into the next question or off the bottom of the page (and don't get too close to the bottom
    %%% either, please!)

@@

% mark option as correct by using \CorrectChoice
\begin{checkboxes}
  \choice True
  \choice False
\end{checkboxes}

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{100pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    %%% run into the next question or off the bottom of the page (and don't get too close to the bottom
    %%% either, please!)

@@

% mark option as correct by using \CorrectChoice
\begin{checkboxes}
  \choice True
  \choice False
\end{checkboxes}

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{175pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    %%% run into the next question or off the bottom of the page (and don't get too close to the bottom
    %%% either, please!)

>>>>

% Student 1
\fbox{
  \begin{minipage}{\textwidth}
    \vspace{0.75cm}
    \makebox[\textwidth]{\large Full Name: Cheung, Hei Shing\enspace\hrulefill}\\[0.75cm]
    \makebox[\textwidth]{\large Student number: 1010907823\enspace\hrulefill}\\
  \end{minipage}
}

@@

% Student 2
\fbox{
  \begin{minipage}{\textwidth}
    \vspace{0.75cm}
    \makebox[\textwidth]{\large Full Name: Lin, Zhiyue\enspace\hrulefill}\\[0.75cm]
    \makebox[\textwidth]{\large Student number: 1010900759\enspace\hrulefill}\\
  \end{minipage}
}

@@

    %%% Your work goes here!  
   \paragraph{} We prove that $B = \varnothing$. Assume, for the sake of contradiction, that $B \neq \varnothing$. Then there exists a point $(a,b,c) \in B$ such that
       $\mathcal{B}_1$, $\mathcal{B}_2$, and $\mathcal{B}_3$ are \textbf{TRUE}. Thus:
       \begin{itemize}
        \item For all $\beta \in \mathbb{R}$, $\beta\mathcal{B}_2: 11\beta a + 7\beta b + 3\beta c = 15\beta$ is \textbf{TRUE}; also
        \item $\mathcal{B}_3$ is \textbf{TRUE}. 
       \end{itemize}
    Hence, $\mathcal{B}_3 - \beta \mathcal{B}_2$ is \textbf{TRUE} for all $\beta \in \mathbb{R}$. This implies there exist $(a,b,c)$ s.t.: $3a + 2b + c = 5$ is \textbf{TRUE}. It follows from $\mathcal{A}_3: 3a + 2b + c = 5$ and that $\mathcal{B}_2 = \mathcal{A}_2$ and that $\mathcal{B}_1 = \mathcal{A}_1$ are all \textbf{TRUE}. Hence $(a,b,c) \in A$. Thus, $A \neq \varnothing$, a contradiction. Therefore, $B = \varnothing$.

@@

   \textcolor{black}{ \underline{case 2: $B = \varnothing$} }
   %%% Do not change the height of this box. Your work must fit inside it.
  \makenonemptybox{130pt}{
   %%% Your work goes here!  
   \paragraph{} We prove that $A = \varnothing$. Assume, for the sake of contradiction, that $A \neq \varnothing$. Then there exists a point $(a,b,c) \in A$ such that $\mathcal{A}_1$, $\mathcal{A}_2$, and $\mathcal{A}_3$ are \textbf{TRUE}. Thus:
       \begin{itemize}
        \item For all $\beta \in \mathbb{R}$, $\beta\mathcal{A}_2: 11\beta a + 7\beta b + 3\beta c = 15\beta$ is \textbf{TRUE}; also
        \item $\mathcal{A}_3$ is \textbf{TRUE}. 
       \end{itemize}
    Hence, $\mathcal{B}_3 = \mathcal{A}_3 + \beta \mathcal{A}_2$ is \textbf{TRUE} for all $\beta \in \mathbb{R}$. It follows from $\mathcal{A}_2 = \mathcal{B}_2$ and that $\mathcal{A}_1 = \mathcal{B}_1$ are all \textbf{TRUE}. Hence $(a,b,c) \in B$. Thus, $B \neq \varnothing$, a contradiction. Therefore, $A = \varnothing$.
% end of your answer to case 2 unless you need to continue the answer on page 4
}

@@

   %%% Do not change the height of this box. Your work must fit inside it.
  \makenonemptybox{25pt}{ 
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    $\alpha \in \mathbb{R}$. It can be any real number.
    %%% end of your answer    
  }

@@

  \subpart Under what conditions on $\alpha$ is $C \subseteq A$? \textit{No justification needed,
just one complete sentence.} \vspace{.15in}
\makenonemptybox{25pt}{ 
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    $\alpha \neq 0$. It can be any non zero real number.
    %%% end of your answer    
  }

@@

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{200pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    \paragraph{} We have $\mathcal{A}_i = \mathcal{B}_i$ for all $i \neq i_0$ and $\mathcal{B}_{i_0} = \alpha \mathcal{A}_{i_0}$. Given nonempty $A,\, B$, we have:
    \begin{equation*}
      \mathcal{A}_{i_0} \text{ is \textbf{TRUE}} \implies \alpha \mathcal{A}_{i_0} \text{ is \textbf{TRUE}} \implies \mathcal{B}_{i_0} \text{ is \textbf{TRUE}}.
    \end{equation*}
    Therefore, $\mathcal{A}$ and $\mathcal{B}$ have the same set of solutions.

@@

%%% Do not change the height of this box. Your work must fit inside it.
\makenonemptybox{400pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    \paragraph{Additve Axioms}
    \begin{enumerate}
      \item By assumption, $\V_0$ is closed under vector addition. Thus, for all $\mathbf{u}, \mathbf{v} \in \V_0$, $\mathbf{u} + \mathbf{v} \in \V_0$.
      \item By assumption, $\V_0$ has the same vector addition as $\V$ and $\V$ is a vetor space. Thus, for all $\mathbf{u}, \mathbf{v}, \mathbf{w} \in \V_0$, $(\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})$.
      \item By assumption, $\V_0$ contains $\mathbf{0}$ and $\V$ is a vector space. Thus, for all $\mathbf{u} \in \V_0 \subseteq \V$, $\mathbf{u} + \mathbf{0} = \mathbf{u}$.
      \item For all $\textbf{u} \in \V_0 \subseteq \V$, a vector space. Under the usual scalar multiplication, $0\textbf{u} = \mathbf{0}$. With $(1 + (-1)) = 0$, we have:
      \begin{equation*}
        \begin{aligned}
          1\textbf{u} + (-1)\textbf{u} &= (1 + (-1))\textbf{u} \\
          &= 0\textbf{u} \\
          &= \mathbf{0}.
        \end{aligned}
      \end{equation*}
      Since $\V_0$ is closed under scalar multiplication, $(-1)\textbf{u} \in \V_0$. Thus, $\V_0$ contains the additive inverse of $\textbf{u}$.
      \end{enumerate}
    \paragraph{Scalar Multiplication Axioms}
    \begin{enumerate}
      \item By assumption, $\V_0$ is closed under scalar multiplication. Thus, for all $c \in \mathbb{R}$ and $\textbf{u} \in \V_0$, $c\textbf{u} \in \V_0$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $c, d \in \mathbb{R}$ and $\textbf{u} \in \V_0 \subseteq \V$, $(cd)\textbf{u} = c(d\textbf{u})$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $c \in \mathbb{R}$ and $\textbf{u}, \textbf{v} \in \V_0 \subseteq \V$, $c(\textbf{u} + \textbf{v}) = c\textbf{u} + c\textbf{v}$.
      \item By assumption, $\V_0$ has the same scalar multiplication as $\V$ and $\V$ is a vector space. Thus, for all $\textbf{u} \in \V_0 \subseteq \V$, $1\textbf{u} = \textbf{u}$.
    \end{enumerate}

@@

 % mark option as correct by using \CorrectChoice
\begin{checkboxes}
  \choice True
  \CorrectChoice False
\end{checkboxes}

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{150pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    Pick $f \in \V$ such that there exist $x_0 \in [2,3]$, $f(x_0) \neq 0$. Choose real number $c<0$, then $cf(x_0) > 0$, hence $c\cdot f \notin \V$. Thus, $\V$ is not closed under scalar multiplication. Therefore, $\V$ is not a vector space over $\mathbb{R}$.

@@

% mark option as correct by using \CorrectChoice
\begin{checkboxes}
  \choice True
  \CorrectChoice False
\end{checkboxes}

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{100pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    Pick $p, q \in \V$ for which $A, -A \in \mathbb{R}$ such that $p(x) = Ax^n$ and $q(x) = -Ax^n$. Then $p(x) + q(x) = A_nx^n + (-A_n)x^n = 0x^n = 0$. However, 0 is not a polynomial of degree exactly $n$. Thus, $\V$ is not closed under vector addition. Therefore, $\V$ is not a vector space over $\mathbb{R}$.

@@

% mark option as correct by using \CorrectChoice
\begin{checkboxes}
  \CorrectChoice True
  \choice False
\end{checkboxes}

 %%% Do not change the height of this box. Your work must fit inside it.
 \makenonemptybox{175pt}{
    %%% Your work goes here!  It is your responsibility to trim down your answer so that it doesn't 
    Given that $^2\mathbb{R}^2$ is a vector space, the set of $2 \times 2$ upper triangular real matrices is a subset of $^2\mathbb{R}^2$. Thus, we prove that $\V$ is a vector space of $^2\mathbb{R}^2$ by showing subspace test holds.
    \begin{enumerate}
      \item $\mathbf{0} \in \V$: $\mathbf{0}$ is an upper triangular matrix with $\textbf{0} = \begin{bmatrix}
        0 & 0 \\
        0 & 0
      \end{bmatrix}$. Given usual entry-wise addition, for all $\textbf{A} \in \V$, $\textbf{A} + \textbf{0} = \begin{bmatrix}
        a_{11} + 0 & a_{12} + 0 \\
        0 & a_{22} + 0
      \end{bmatrix} = \textbf{A}$. Thus, $\mathbf{0} \in \V$.
      \item Closure under addition: Let $A, B \in \V$. Then $A + B = \begin{bmatrix}
        a_{11} + b_{11} & a_{12} + b_{12} \\
        0 & a_{22} + b_{22}
      \end{bmatrix}$. So $A + B$ is upper triangular, and $A + B \in \V$.
      \item Closure under scalar multiplication: Let $A \in \V$ and $c \in \mathbb{R}$. Then $cA = \begin{bmatrix}
        ca_{11} & ca_{12} \\
        0 & ca_{22}
      \end{bmatrix}$. So $cA$ is upper triangular, and $cA \in \V$.
    \end{enumerate}
